Intelligent Quadcopter for IARC 2018

### 2018-06-01 IARC_Paper_2018/Paper.tex
too many lines or something
Graph changes

	\begin{figure}[!htbp]
	\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
		% Place nodes
		\node [block] (battery) {Battery};
		\node [block, below of=battery] (siphon) {Power siphon};
		\node [block, below of=siphon] (Pixhawk) {Pixhawk};
		\node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
		\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
		\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
		\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
		\node [block, below right of=Jetson] (Camera) {Cameras};
		\node [block, below left of=Jetson] (2dLidar) {2D LiDAR};
		\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
		\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
		\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
		% Draw edges
		\path [line] (battery) -- (siphon);
		\path [line] (siphon) -- (Pixhawk);
		\path [line] (battery) -- (PDB);
		\path [line] (PDB) -- (ESCs);
		\path [line] (battery) -- (Jetson);
		\path [line, dashed] (Camera) -- (Jetson);
		\path [line, dashed] (2dLidar) -- (Jetson);
		\path [line, dashed] (Flow) -- (Pixhawk);
		\path [line, dashed] (Jetson) -- (Pixhawk);
		\path [line, dashed] (LiDAR) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (Telemetry);
		\path [line, dashed] (Spektrum) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (ESCs);
		\path [line] (ESCs) -- (Motors);
	\end{tikzpicture}
	\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
	\end{center}
	\end{figure}

@@

		This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.

>>>>

	\begin{figure}[!htbp]
	\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
		% Place nodes
		\node [block] (electronicsBattery) {Electonics Battery};
		\node [block, right of=electronicsBattery, xshift=2.5cm] (motorBattery) {Motor Battery};
		\node [block, below of=electronicsBattery] (siphon) {Power siphon};
		\node [block, below of=siphon] (Pixhawk) {Pixhawk};
		\node [block, below right of=electronicsBattery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
		\node [block, below left of=electronicsBattery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
		\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
		\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
		\node [block, below right of=Jetson, yshift=-.5cm] (Camera) {Cameras};
		\node [block, below left of=Jetson, yshift=-.5cm] (2dLidar) {2D LiDAR};
		\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
		\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
		\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
		% Draw edges
		\path [line] (electronicsBattery) -- (siphon);
		\path [line] (siphon) -- (Pixhawk);
		\path [line] (motorBattery) -- (PDB);
		\path [line] (PDB) -- (ESCs);
		\path [line] (electronicsBattery) -- (Jetson);
		\path [line, dashed] (Camera) -- (Jetson);
		\path [line, dashed] (2dLidar) -- (Jetson);
		\path [line, dashed] (Flow) -- (Pixhawk);
		\path [line, dashed] (Jetson) -- (Pixhawk);
		\path [line, dashed] (LiDAR) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (Telemetry);
		\path [line, dashed] (Spektrum) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (ESCs);
		\path [line] (ESCs) -- (Motors);
	\end{tikzpicture}
	\caption*{Flowchart of quadcopter electronics \\ \scriptsize *Solid arrows indicate power while dashed lines indicate power+data}
	\end{center}
	\end{figure}

@@
